### 2015-07-25 simulation.Rmd
testing shape

## residuals for 9-5 Tmers
```{r resids_9_5, results="asis", fig.align='center'}
resids <- counts_table(in_longwin=9, in_shortwin=5, half_n_show=20)
counts_plot(resids)
```

>>>>

## residuals for 3-3 Tmers
```{r resids_3_3, results="asis", fig.align='center'}
resids <- counts_table(in_longwin=3, in_shortwin=3, half_n_show=20)
counts_plot(resids)
```

## residuals for 5-5 Tmers
```{r resids_5_5, results="asis", fig.align='center'}
resids <- counts_table(in_longwin=5, in_shortwin=5, half_n_show=20)
counts_plot(resids)
```
